```{r, echo=FALSE}
knitr::opts_chunk$set(  echo=TRUE, eval=FALSE)
library(mgcv)
library(tidyverse)
library(brms);library(ggplot2);library(scales)
library(data.table)
library(directlabels)
```

# Estimating Desktop Browser Market Size

Desktop Firefox has been losing users for the past few years and we
have also been losing market share. We've generally attributed this to
a combination of Chrome taking our users and the generally declining
state of the desktop market.

We can use the combination of our user numbers (MAU), which we know,
and an external estimate of our market share to estimate the overall
size of the market.

```{r eval=TRUE, echo=FALSE}
ms <- read.delim("browser-ww-monthly-200901-201910.csv", header=TRUE, sep=",")
mau <- read.delim("mau-reduced.csv", header=TRUE, sep=",")
df <- data.frame(date=as.Date(mau$day,"%Y-%m-%d"), share=ms$Firefox/100, mau=mau$mau)
df <- filter(df, df$date >= as.Date("2017-01-01"))
df$size <- df$mau/df$share
df$mau.normal <- df$mau/df$mau[1]
df$share.normal <- df$share/df$share[1]
df.long <- gather(df, key="Source", value="Frac", mau.normal, share.normal)
```

Fhe following figure shows the decline of MAU and market share over
the 2 years ending in January 2019. The MAU data comes from our
own telemetry and the market share data comes from StatCounter.
Each of these is normalized to the start of the period. 
Note that market share is declining faster than MAU, though
clearly something is wrong with the beginning of the MAU series.


```{r eval=TRUE,fig.width=6, fig.height=4}
ggplot(df.long) + geom_line(mapping=aes(x=date, y=Frac, color=Source))
```

We can get an estimate of the size of the market by dividing MAU
by our share of the market, giving us the graph below. Based on
this data, desktop market size has actually increased over
this period.


```{r eval=TRUE,fig.width=6, fig.height=4}
ggplot(df) + geom_line(mapping=aes(x=date, y=size))
```